Discrete Quantum Theories and Computing

### 2019-01-10 dissertation.tex
dissertation.lyx Preface and "Chapter 6 Further Discussion" Updating...

\begin{preface*}
\begin{itemize}
\item The latest version of this thesis is in GitHub: \code{https://git.io/fxbuG}
\item Its source code is typeset using \LyX ~\cite{LyX} in: \code{https://git.io/fxbuE}
\item Any comments can be left in the Issue part of the GitHub Repository:
\code{https://git.io/fxbug}
\end{itemize}
\end{preface*}

@@

\begin{comment}
When people proved the original Gleason theorem, people usually exploited
the geometrical structure of real 3-dimensional Hilbert space \cite{gleason1957,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
Since our finite-precision extension of the Gleason theorem only applies
on a class of QIVPMs, we might want to ask how to modify these geometrical
arguments to have a Gleason-type theorem for general QIVPMs. We will
further study the tensor product structure among QIVPMs which is essential
for defining product and entangled states, and serves the basis to
discuss quantum nonlocality~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and quantum computing with QIVPMs. Finally, we want to improve the
discrete quantum theories to consider QIVPMs over finite fields in
future research.
\end{comment}
As we discussed in the previous section, the finite-precision extension
of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
only applies on the QIVPMs composted by interval maps $f:\left[0,1\right]\rightarrow\mathscr{I}$
and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$,
where the maximum length of intervals in $\mathscr{I}$ is an important
. In this case, the states consistent with the composition $f\circ\muB_{\rho}$
is bounded by . While the QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
is not in this class, it is too wild to have a non-empty core, and
the maximum length of its intervals $\mathscr{I}_{0}$ is $1$, the
longest length of all possible intervals. This suggests us to ask
if we shirk the maximum length of intervals alone, whether this ill-behaved
QIVPMs disappears. More precisely, we have the following question.

@@

\todo{Add a two-page conclusion chapter which could include further
discussion, but it can be only a few sentences? }\todo{Discrete
Schrödinger equation? And its relation with Grover's algorithm? }\todo{Notice
that in differential geometry, Killing–Hopf theorem asserts that having
positive constant curvature guarantees a manifold is essentially a
sphere, but say little things even if the curvature has only small
deviation from constant. Since a quantum probability measure is glued
by classical probability measures, like a manifold. When their relations
are exact, Gleason's theorem asserts that a quantum probability measure
can essentially induced by the Born rule, but they can be wild when
we move on to interval-valued situation! }
\end{comment}

>>>>

\begin{preface*}
\begin{itemize}
\item The latest version of this thesis is in GitHub: \code{https://git.io/fxbuG}
\item Its source code is typeset using \LyX ~\cite{LyX} in: \code{https://git.io/fxbuE}
and the exported \LaTeX{} is in \code{https://git.io/fhZBW}.
\item Any comments can be left in the Issue part of the GitHub Repository:
\code{https://git.io/fxbug}
\end{itemize}
Following explains how to compile the PDF from the source:
\begin{enumerate}
\item Clone the document class \code{https://github.com/yuttai/iuphd} in
a location where the system can find.
\item Run \code{xelatex dissertation.tex}.
\item Run \code{biber dissertation}.
\item Run \code{xelatex dissertation.tex} several times until all the references
are resolved.
\end{enumerate}
\end{preface*}

@@

\begin{comment}
When people proved the original Gleason theorem, people usually exploited
the geometrical structure of real 3-dimensional Hilbert space \cite{gleason1957,peres1995quantum,RichmanBridges1999,Hamhalter2013}.
Since our finite-precision extension of the Gleason theorem only applies
on a class of QIVPMs, we might want to ask how to modify these geometrical
arguments to have a Gleason-type theorem for general QIVPMs. We will
further study the tensor product structure among QIVPMs which is essential
for defining product and entangled states, and serves the basis to
discuss quantum nonlocality~\cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and quantum computing with QIVPMs. Finally, we want to improve the
discrete quantum theories to consider QIVPMs over finite fields in
future research.
\end{comment}
As we discussed in the previous section, the finite-precision extension
of the Gleason theorem, Thm.~\ref{thm:Finite-precision-Gleason},
only applies on the QIVPMs composted by interval maps $f:\left[0,1\right]\rightarrow\mathscr{I}$
and quantum probability measures $\muB_{\rho}:\events\rightarrow\left[0,1\right]$,
and the states consistent with the composition $f\circ\muB_{\rho}$
converges to $\rho$ as the maximum length of intervals in $\mathscr{I}$
shrinking to $0$. In contrast, the wildest QIVPM defined in Table~\ref{tab:non-Born-QIVPM}
is not in this class and the maximum length of its intervals $\mathscr{I}_{0}$
is $1$, the longest length of all possible intervals. This doesn't
rule out the possibility that shirking the maximum length of intervals
itself could result QIVPMs with non-empty cores. More precisely, we
have the following question.

@@

\todo{Add a two-page conclusion chapter which could include further
discussion, but it can be only a few sentences? }\todo{Discrete
Schrödinger equation? And its relation with Grover's algorithm? }\todo{Notice
that in differential geometry, Killing–Hopf theorem asserts that having
positive constant curvature guarantees a manifold is essentially a
sphere, but say little things even if the curvature has only small
deviation from constant. Since a quantum probability measure is glued
by classical probability measures, like a manifold. When their relations
are exact, Gleason's theorem asserts that a quantum probability measure
can essentially induced by the Born rule, but they can be wild when
we move on to interval-valued situation! }
\end{comment}
To understand how difficult this question could be,
